### 2018-08-29 case_for_support.tex
Added hotel chain

  \begin{itemize}
  \item {\bf Thai AirAsia} is part of the AirAsia group, which is the largest budget airline operating in South East Asia. They are renowned among the air industry for their high levels of aircraft utility (i.e., maximising the time a plane is in the air, and thus generating revenue). A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while they wait for the delivery of spare parts from various warehouses. This waiting could be reduced if AirAsia were able to predict when parts were likely to require replacement, and then act upon this when the aircraft was located at an airport with a parts warehouse. AirAsia engineers will share their flight data with our team so that we can adapt the techniques we have developed to identify rare sources in astronomy to better predict rare instances where parts require replacement. To assist with this development, Thai AirAsia have offered to host the students working on the project on a work-experience placement.
  \item {\bf Thaweeyont} is a chain of bricks-and-mortar stores that specialise in electronic household appliances, furniture and motorcycles/scooters. They have expanded rapidly over the past decade, and are now looking to move into more locations. A problem they face when opening new stores is how to predict the types of customer (sex, age, dispoable income, etc.) that are likely to visit the new store, which has knock-on effects on how to stock the new store. Thaweeyont would like a work with small group of students and researchers to investigate how we can adapt the work conducted during the first phase of our GCRF project (see Thanapiriya) to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
  \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand.
\end{itemize}

>>>>

  \begin{itemize}
  \item {\bf Thai AirAsia} is part of the AirAsia group, which is the largest budget airline operating in South East Asia. They are renowned among the air industry for their high levels of aircraft utility (i.e., maximising the time a plane is in the air, and thus generating revenue). A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while they wait for the delivery of spare parts from various warehouses. This waiting could be reduced if AirAsia were able to predict when parts were likely to require replacement, and then act upon this when the aircraft was located at an airport with a parts warehouse. AirAsia engineers will share their flight data with our team so that we can adapt the techniques we have developed to identify rare sources in astronomy to better predict rare instances where parts require replacement. To assist with this development, Thai AirAsia have offered to host the students working on the project on a work-experience placement.
  %\item {\bf Thaweeyont} is a chain of bricks-and-mortar stores that specialise in electronic household appliances, furniture, and motorcycles/scooters. They have expanded rapidly over the past decade, and are now looking to expand into more locations. A problem they face when opening new stores is how to predict the types of customer (sex, age, dispoable income, etc.) that are likely to visit the new store, which has knock-on effects on how to stock the new store. Thaweeyont would like a work with small group of students and researchers to investigate how we can adapt the work conducted during the first phase of our GCRF project (see Thanapiriya) to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
  \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand. This region is a popular tourist destination, resulting in a particularly competitive hotel market and corresponding thin margins. Deevana has found that various promotions (e.g., reduced tariffs, free services/experiences, etc.) help boost traffic to their hotels, resulting in fewer empty rooms. At present, however, they use a scatter-gun approach to advertise these promotions, whereas more targeted campaigns based on customer need may deliver better results. Deevana wishes for our students to research how machine learning -- in particular clustering analysis -- could be used to better identify different types of customers and test which promotions are most effective at attracting different customer types. In return, our staff and students will gain experience in a developing technology solutions for one of Thailand's most important economic sectors.
  \item {\bf Biophics} is a Center of Excellence for biomedical and health informatics operating out of the Faculty of Tropical Medicine at Mahidol University, Bangkok. They specialise in the collection and analysis of data relating to the incidence and spread of infectious diseases within Thailand. 
\end{itemize}
